|

### 2021-01-28 appendix/appendix.Rmd
add descriptive statistics to appendix

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

@@

```{r setup, echo=FALSE}
plotAMCE <-
    function (x, main = "", xlab = "Change in E[Y]",
              ci = 0.95, colors = NULL,
              xlim = NULL, breaks = NULL,
              labels = NULL, attribute.names = NULL,
              level.names = NULL, label.baseline = TRUE,
              text.size = 11,
              text.color = "black",
              point.size = 0.5, dodge.size = 0.9,
              plot.theme = NULL, plot.display = "all",
              facet.names = NULL,
              facet.levels = NULL,
              group.order = NULL, font.family = NULL,
              tblfy = F, ...) {
        amce_obj <- x
        ylim <- xlim
        pe <- NULL
        se <- NULL
        group <- NULL
        lower <- NULL
        upper <- NULL
        var <- NULL
        printvar <- NULL
        facet <- NULL
        raw_attributes <- names(amce_obj$estimates)
        raw_levels <- lapply(amce_obj$estimates, colnames)
        for (effect in names(raw_levels)) {
            effect_elements <- strsplit(effect, ":")[[1]]
            baseline_interactions <- c()
            for (elem in effect_elements) {
                base_coef <- paste(c(elem, amce_obj$baselines[[elem]]),
                                   collapse = "")
                baseline_interactions <- c(baseline_interactions,
                                           base_coef)
            }
            interaction_str <- paste(baseline_interactions, sep = "",
                                     collapse = ":")
            raw_levels[[effect]] <- c(interaction_str, raw_levels[[effect]])
        }
        if (ci < 1 & ci > 0) {
            zscr <- qnorm(1 - ((1 - ci)/2))
        }
        else {
            cat("Invalid confidence interval -- Defaulting to 95%")
            zscr <- qnorm(1 - ((1 - 0.95)/2))
        }
        if (!is.null(attribute.names)) {
            attribute.names <- unique(attribute.names)
            if (length(attribute.names) != length(raw_attributes)) {
                cat(paste("Error: The number of unique elements in attribute.names ",
                          length(attribute.names), " does not match the attributes in amce object for which estimates were obtained: ",
                          paste(raw_attributes, collapse = ", "), "\n",
                          sep = ""))
                cat("Defaulting attribute.names to attribute names in AMCE object\n")
                attribute.names <- NULL
            }
        }
        if (!is.null(level.names)) {
            names(level.names) <- clean.names(names(level.names))
            for (name in names(level.names)) {
                if (name %in% names(raw_levels)) {
                    if (length(level.names[[name]]) != length(raw_levels[[name]])) {
                        cat(paste("Error: level.names lengths do not match levels for attribute ",
                                  name, "\n", sep = ""))
                        cat(paste("Defaulting level.names for attribute ",
                                  name, " to level names in AMCE object", "\n",
                                  sep = ""))
                        level.names[[name]] <- NULL
                    }
                }
                else {
                    cat(paste("Error: level.names entry ", name,
                              " not in AMCE object. Removing level.names for attribute.",
                              "\n", sep = ""))
                    level.names[[name]] <- NULL
                }
            }
        }
        if (is.null(attribute.names)) {
            attribute.names <- c()
            for (attr in names(amce_obj$estimates)) {
                attr_split <- strsplit(attr, ":")[[1]]
                attr_lookup <- paste(unlist(sapply(attr_split, function(x) amce_obj$user.names[x])),
                                     collapse = ":")
                attribute.names <- c(attribute.names, attr_lookup)
            }
        }
        if (is.null(level.names))
            level.names <- list()
        if (any(!names(raw_levels) %in% names(level.names))) {
            for (attr in names(raw_levels)[!names(raw_levels) %in%
                                           names(level.names)]) {
                attr_split <- strsplit(raw_levels[[attr]], ":")
                level.names[[attr]] <- unlist(lapply(attr_split,
                                                     function(x) paste(sapply(x, function(y) amce_obj$user.levels[y]),
                                                                       collapse = ":")))
            }
        }
        plot.display.opts <- c("all", "unconditional", "interaction")
        if (!is.element(plot.display, plot.display.opts)) {
            stop(paste(c("Error-- plot.display must be once of: ",
                         paste(plot.display.opts, collapse = ", ")), collapse = " "))
        }
        if (!is.null(facet.names)) {
            facet.names <- clean.names(facet.names)
        }
        else if (!is.null(facet.levels)) {
            facet.names <- clean.names(names(facet.levels))
        }
        if (!is.null(facet.names)) {
            facet.names.check <- c()
            for (facet.name in facet.names) {
                if (grepl(":", facet.name))
                    stop("Error-- cannot facet by interaction in current version.")
                if (!facet.name %in% names(amce_obj$estimates) &
                    !facet.name %in% names(amce_obj$cond.estimates)) {
                    stop(paste(c("Error-- cannot find facet name",
                                 facet.name, "in AMCE object output."), collapse = " "))
                }
                else {
                    facet.names.check <- c(facet.names.check, facet.name)
                }
            }
            facet.names <- facet.names.check
        }
        if ((is.null(facet.names)) & (length(amce_obj$respondent.varying) >
                                      0) & (plot.display != "unconditional")) {
            facet.names <- amce_obj$respondent.varying
        }
        if (is.null(facet.names) & plot.display == "interaction") {
            warning("Warning: no facet name or respondent varying characteristic provided to calculate conditional estimates. Will display unconditional only")
            plot.display <- "unconditional"
        }
        if (plot.display == "unconditional" & !is.null(facet.names)) {
            warning("Warning-- plot display is set to unconditional, facet names will be ignored")
            facet.names <- NULL
            facet.levels <- NULL
        }
        if (!is.null(facet.levels)) {
            names(facet.levels) <- clean.names(names(facet.levels))
            for (facet.name in names(facet.levels)) {
                if (facet.name %in% names(amce_obj$baselines)) {
                    facet.levels[[facet.name]] <- clean.names(facet.levels[[facet.name]])
                    if (facet.name %in% names(amce_obj$estimates) &&
                        is.element(amce_obj$baselines[[facet.name]],
                                   facet.levels[[facet.name]])) {
                        stop(paste(c("Error: Facet level \"", as.character(amce_obj$baselines[[facet.name]]),
                                     "\" is the baseline level of a profile varying attribute. Please provide alternative facet level or use defaults."),
                                   collapse = ""))
                    }
                    if (is.null(names(facet.levels[[facet.name]]))) {
                        fac.levs <- sapply(facet.levels[[facet.name]],
                                           function(x) paste(facet.name, x, sep = ""))
                        names(facet.levels[[facet.name]]) <- sapply(fac.levs,
                                                                    USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
                    }
                }
                else if (is.null(names(facet.levels[[facet.name]]))) {
                    names(facet.levels[[facet.name]]) <- as.character(facet.levels[[facet.name]])
                }
            }
        }
        if (is.null(facet.levels))
            facet.levels <- list()
        if (any(!facet.names %in% names(facet.levels))) {
            for (facet.name in facet.names[!facet.names %in% names(facet.levels)]) {
                if (facet.name %in% names(amce_obj$baselines)) {
                    if (facet.name %in% names(amce_obj$estimates)) {
                        fac.levs <- colnames(amce_obj$estimates[[facet.name]])
                    }
                    else {
                        fac.levs <- colnames(amce_obj$cond.estimates[[facet.name]])
                    }
                    facet.levels[[facet.name]] <- sub(facet.name,
                                                      "", fac.levs)
                    facet.levels[[facet.name]] <- c(amce_obj$baselines[[facet.name]],
                                                    facet.levels[[facet.name]])
                    fac.levs <- c(paste(facet.name, amce_obj$baselines[[facet.name]],
                                        sep = ""), fac.levs)
                    names(facet.levels[[facet.name]]) <- sapply(fac.levs,
                                                                USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
                }
                else if (facet.name %in% names(amce_obj$continuous)) {
                    facet.levels[[facet.name]] <- amce_obj$continuous[[facet.name]]
                }
            }
        }
        covariate.values <- list()
        for (var in names(facet.levels)) {
            if (var %in% amce_obj$respondent.varying) {
                covariate.values[[var]] <- facet.levels[[var]]
            }
        }
        d <- data.frame(pe = c(), se = c(), upper = c(), lower = c(),
                        var = c(), printvar = c(), group = c(), facet = c())
        if (plot.display != "interaction") {
            if (plot.display == "all") {
                uncond.facet.name <- "Unconditional"
            }
            else {
                uncond.facet.name <- NA
            }
            if (plot.display == "all" && !is.null(facet.names)) {
                attr_remove <- c()
                for (facet.name in facet.names[!is.element(facet.names,
                                                           amce_obj$respondent.varying)]) {
                    attr_remove1 <- raw_attributes[grepl(":", raw_attributes)]
                    attr_remove1 <- attr_remove1[grepl(facet.name,
                                                       attr_remove1)]
                    attr_remove <- c(attr_remove, attr_remove1)
                }
                raw_attributes <- raw_attributes[!is.element(raw_attributes,
                                                             attr_remove)]
            }
            for (i in 1:length(raw_attributes)) {
                attr_name <- raw_attributes[i]
                print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
                                                             raw_attributes[i])]
                d_head <- data.frame(pe = NA, se = NA, upper = NA,
                                     lower = NA, var = attr_name, printvar = paste(print_attr_name,
                                                                                   ":", sep = ""), group = "<NA>", facet = uncond.facet.name)
                d <- rbind(d, d_head)
                for (j in 1:length(raw_levels[[attr_name]])) {
                    level_name <- raw_levels[[attr_name]][j]
                    print_level_name <- level.names[[attr_name]][j]
                    if (j == 1) {
                        if (label.baseline) {
                            print_level_name <- paste("(Baseline = ",
                                                      print_level_name, ")", sep = "")
                        }
                        d_lev <- data.frame(pe = NA, se = NA, upper = NA,
                                            lower = NA, var = level_name, printvar = paste("   ",
                                                                                           print_level_name, sep = ""), group = print_attr_name,
                                            facet = uncond.facet.name)
                    }
                    else {
                        val_pe <- amce_obj$estimates[[attr_name]][1,
                                                                  level_name]
                        val_se <- amce_obj$estimates[[attr_name]][2,
                                                                  level_name]
                        upper_bnd <- val_pe + zscr * val_se
                        lower_bnd <- val_pe - zscr * val_se
                        d_lev <- data.frame(pe = val_pe, se = val_se,
                                            upper = upper_bnd, lower = lower_bnd, var = level_name,
                                            printvar = paste("   ", print_level_name,
                                                             sep = ""), group = print_attr_name, facet = uncond.facet.name)
                    }
                    d <- rbind(d, d_lev)
                }
            }
        }
        if (plot.display != "unconditional" & !is.null(facet.names)) {
            for (facet.name in facet.names) {
                print_facet_name <- amce_obj$user.names[[facet.name]]
                all_req_vars <- attr(terms(amce_obj$formula), "term.labels")
                all_mod <- unlist(sapply(all_req_vars, function(x) {
                    y <- strsplit(x, ":")[[1]]
                    if (any(y == facet.name))
                        x
                }))
                all_mod <- unlist(sapply(all_mod, function(x) {
                    subs <- strsplit(x, ":")[[1]]
                    subs <- subs[is.element(subs, names(amce_obj$estimates))]
                    subs <- subs[subs != facet.name]
                    if (length(subs) > 0)
                        paste(subs, collapse = ":")
                }))
                if (length(all_mod) == 0) {
                    stop(paste(c("Error: Facet variable", facet.name,
                                 "not interacted with profile attributes"),
                               collapse = " "))
                }
                all_mod <- unique(all_mod)
                if (is.element(facet.name, names(amce_obj$estimates))) {
                    facet.start <- 2
                }
                else {
                    facet.start <- 1
                }
                for (k in facet.start:length(facet.levels[[facet.name]])) {
                    facet_lev <- facet.levels[[facet.name]][k]
                    if (is.element(facet.name, names(amce_obj$estimates))) {
                        print_facet_level <- paste(c("ACIE", paste(c(print_facet_name,
                                                                     names(facet.levels[[facet.name]])[k]), collapse = " = ")),
                                                   collapse = "\n")
                    }
                    else {
                        print_facet_level <- paste(c("Conditional on",
                                                     paste(c(print_facet_name, names(facet.levels[[facet.name]])[k]),
                                                           collapse = " = ")), collapse = "\n")
                    }
                    for (mod_var in all_mod) {
                        print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
                                                                     mod_var)]
                        d_head <- data.frame(pe = NA, se = NA, upper = NA,
                                             lower = NA, var = mod_var, printvar = paste(print_attr_name,
                                                                                         ":", sep = ""), group = "<NA>", facet = print_facet_level)
                        d <- rbind(d, d_head)
                        if (facet.name %in% names(amce_obj$estimates)) {
                            inter_coef <- paste(sort(c(mod_var, facet.name)),
                                                collapse = ":")
                            estimate.source <- amce_obj$estimates[[inter_coef]]
                            estimate.source <- estimate.source[, grep(paste0(facet.name,
                                                                             facet_lev), colnames(estimate.source))]
                        }
                        else {
                            estimate.source <- get.conditional.effects(amce_obj,
                                                                       covariate.values, facet.name, facet_lev,
                                                                       mod_var)
                        }
                        mod_vars <- strsplit(mod_var, ":")[[1]]
                        for (p in 1:length(raw_levels[[mod_var]])) {
                            mod_coef <- raw_levels[[mod_var]][p]
                            mod_coefs <- strsplit(mod_coef, ":")[[1]]
                            for (lev in 1:length(mod_coefs)) {
                                mod_lev <- sub(mod_vars[lev], "", mod_coefs[lev])
                            }
                            print_level_name <- level.names[[mod_var]][p]
                            if (p == 1) {
                                if (label.baseline) {
                                    print_level_name <- paste("(Baseline = ",
                                                              print_level_name, ")", sep = "")
                                }
                                d_lev <- data.frame(pe = NA, se = NA, upper = NA,
                                                    lower = NA, var = mod_coef, printvar = paste("   ",
                                                                                                 print_level_name, sep = ""), group = print_attr_name,
                                                    facet = print_facet_level)
                            }
                            else {
                                val_pe <- estimate.source[1, p - 1]
                                if (!is.na(val_pe)) {
                                    val_se <- estimate.source[2, p - 1]
                                    upper_bnd <- val_pe + zscr * val_se
                                    lower_bnd <- val_pe - zscr * val_se
                                }
                                else {
                                    val_se <- upper_bnd <- lower_bnd <- NA
                                }
                                d_lev <- data.frame(pe = val_pe, se = val_se,
                                                    upper = upper_bnd, lower = lower_bnd,
                                                    var = mod_coef, printvar = paste("   ",
                                                                                     print_level_name, sep = ""), group = print_attr_name,
                                                    facet = print_facet_level)
                            }
                            d <- rbind(d, d_lev)
                        }
                    }
                }
            }
        }
        else {
            d <- d[, -which(colnames(d) == "facet")]
        }
        if (is.null(ylim)) {
            max_upper <- max(d$upper, na.rm = T) + 0.05
            min_lower <- min(d$lower, na.rm = T) - 0.05
            ylim <- c(min_lower, max_upper)
            d[is.na(d)] <- max_upper + 100
        }
        else {
            d[is.na(d)] <- max(ylim) + 100
        }
        d$group[d$group == "<NA>"] <- NA
        if (!is.null(facet.names))
            d$facet[d$facet == "<NA>"] <- NA
        d$var <- factor(d$var, levels = unique(d$var)[length(d$var):1])
        if (!is.null(facet.names)) {
            d$facet <- factor(d$facet, levels = unique(d$facet))
        }
        if (!is.null(group.order)) {
            n.row <- length(unique(as.character(d$var)))
            order.var <- vector("character", length = n.row)
            i <- 1
            while (i < n.row) {
                for (j in group.order) {
                    order.var[i] <- unique(as.character(d$var[d$var ==
                                                                  gsub(" ", "", j)]))
                    i <- i + 1
                    temp.d <- d
                    temp.d$group <- gsub(" ", "", temp.d$group)
                    temp.d <- subset(temp.d, group == gsub(" ", "",
                                                           j))
                    temp.var <- unique((as.character(temp.d$var)))
                    order.var[i:(i + length(temp.var) - 1)] <- temp.var
                    i <- i + length(temp.var)
                }
            }
            order.var <- rev(order.var)
            order.df <- data.frame(order.var, 1:length(order.var))
            colnames(order.df) <- c("var", "order")
            d$var <- factor(d$var, levels = order.var)
            d <- merge(d, order.df, by.x = "var", by.y = "var", suffixes = c("",
                                                                             ""))
        }
        levs <- as.character(d$printvar)
        levs <- gsub('organizations', 'organisations', levs)
        d$printvar <- factor(levs, levels = levs)
        if(tblfy) {
            return(d)
        }
        p = ggplot(d, aes(y = pe, x = var, colour = group))
        p = p + coord_flip(ylim = ylim)
        p = p + geom_hline(yintercept = 0, size = 0.5, colour = "black",
                           linetype = "dotted")
        p = p + geom_pointrange(aes(ymin = lower, ymax = upper),
                                position = position_dodge(width = dodge.size), size = point.size)
        if (!is.null(facet.names)) {
            p = p + facet_wrap(~facet)
        }
        if (is.null(breaks) & is.null(labels)) {
            p = p + scale_y_continuous(name = xlab)
        }
        else if (is.null(breaks) & !is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, labels = labels)
        }
        else if (!is.null(breaks) & is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, breaks = breaks)
        }
        else if (!is.null(breaks) & !is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, breaks = breaks,
                                       labels = labels)
        }
        if (!is.null(group.order)) {
            fix.xlabs.df <- d[!duplicated(d$var), ]
            fix.xlabs <- fix.xlabs.df[order(-fix.xlabs.df$order),
                                      ]$printvar
        }
        else {
            fix.xlabs <- as.character(d$printvar)[!duplicated(d$var)]
        }
        p = p + scale_x_discrete(name = "", labels = fix.xlabs[length(fix.xlabs):1])
        if (!is.null(main)) {
            if (main != "") {
                p = p + ggtitle(main)
            }
        }
        if (is.null(colors)) {
            p = p + scale_colour_discrete(" ")
        }
        else if (is.vector(colors)) {
            cPal <- rep(colors, ceiling(length(unique(d$group))/length(colors)))
            p = p + scale_colour_manual(values = cPal)
        }
        else {
            cat("Error: 'colors' must be a vector. Using default colors\n")
            p = p + scale_colour_discrete(" ")
        }
        if (is.null(plot.theme)) {
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else if (is.null(class(plot.theme))) {
            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else if (class(plot.theme)[1] != "theme") {
            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else {
            p = p + plot.theme
            print(p)
        }
        if (length(covariate.values) > 1) {
            resp.message <- c("Note:")
            for (this.var in names(covariate.values)) {
                resp.message <- paste(c(resp.message, " For AMCE and ACIE conditional on ",
                                        this.var, ", "), collapse = "")
                other.vars <- names(covariate.values)[names(covariate.values) !=
                                                          this.var]
                other.levels <- c()
                for (var in other.vars) {
                    other.levels <- c(other.levels, paste(c(var,
                                                            " will be held at level \"", names(covariate.values[[var]])[1],
                                                            "\""), collapse = ""))
                }
                other.levels <- paste(other.levels, collapse = ", and ")
                resp.message <- c(resp.message, other.levels, ".")
                resp.message <- paste(resp.message, collapse = "")
            }
            cat(resp.message, "\n")
        }
    }
```

# Descriptive Statistics
\label{sec:descriptive}

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

From October 1 to December 5, 2018, we ran an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. The survey proceeded in two steps.

We collected information on Latin American elites. The target was:

1. Members of the Executive branch
2. Members of the Legislative branch
3. Civil society
4. Academics

For each profile, in each country, we aimed at surveying:

1. 10 members of the Executive branch
2. 10 members of the Legislative branch
3. 15 Civil society
4. 15 Academics

To do so, we built a prospective respondents dataset with ten times these members for each country. Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other climate
change-related problems.

After finishing this dataset, we started the surveying stage. From November 12 to December 5, we ran the survey by contacting elite members by phone or by email. We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers. Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.

# Descriptive Statistics \label{sec:descstats}

The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

# Country
tab <- data.frame(table(aux$countryOrigin))
names(tab) <- c('Country', 'Frequency')
p<- ggplot(data = tab, aes(x = Country, y = Frequency)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 50, linetype = "dashed", color = "black") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$Country, y = tab$Frequency + 2)
p

# Elite type
tab <- data.frame(table(aux$groupOrigin))
names(tab) <- c('Group Origin', 'Frequency')
p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
  geom_bar(stat = "identity") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$`Group Origin`, y = tab$Frequency + 5)
p
```

As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru. To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.

Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by those from the Executive and Legislative branches. The data collection for members of the Legislative branch was below the original target, but above the minimum mark of 5 for each country. This is expected, given the difficulty of accessing these elite members.

In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities. This is also in line with our expectations, as elite members are assumed to gravitate around capital cities and large urban centers.

# Frequency of Features Selected by Each Attribute \label{sec:features}

The figures below display the feature frequency for each attribute, by each task.

```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
aux <- cj %>%
  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
  unique()

# Who makes the rules
tab <- data.frame(table(aux$`Who makes the rules?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('Who makes the rules?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are conflicts resolved?
tab <- data.frame(table(aux$`How are conflicts resolved?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are conflicts resolved?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# What punishments do they use?
tab <- data.frame(table(aux$`What punishments do they use?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('What punishments do they use?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 40) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are repeated violations punished?
tab <- data.frame(table(aux$`How are repeated violations punished?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are repeated violations punished?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are costs distributed?
tab <- data.frame(table(aux$`How are costs distributed?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are costs distributed?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How often will the agreement be renegotiated?
tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How often will the agreement be renegotiated?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*. This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.

# Code for the Main Paper

The code for Figure 2 of the paper follows below. We also include the point estimates in companion tables.

```{r codefig2}
## Main plot
# Main estimation equation
fm <- selected ~ `Who makes the rules?` +
  `How are conflicts resolved?` +
  `What punishments do they use?` +
  `How are repeated violations punished?` +
  `How are costs distributed?` +
  `How often will the agreement be renegotiated?`

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0 = 0.5)

myFaces <- c(rep('plain', 5), "bold",
             rep('plain', 4), "bold",
             rep('plain', 3), "bold",
             rep('plain', 4), "bold",
             rep('plain', 5), "bold",
             rep('plain', 5), "bold")

p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) + ggplot2::theme(
    legend.position = "none",
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    axis.text.y = element_text(face=myFaces, size = 11)) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 1, height = 0, na.rm = TRUE,
                            position = ggstance::position_dodgev(height = 1))
p

ggsave(filename = 'MM_all.pdf', plot = p, width = 8, height = 6)

# Table
table_mm <- function(mms, capt) {
  dfr <- data.frame(feature = mms[,c(4)],
             round(mms[,c(5,6,8,9,10)], digits=3))
  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
                'P-Value', 'Lower', 'Upper')
  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
    kable_styling(font_size = 10) %>%
    group_rows('Who makes the rules?', 1, 5) %>%
    group_rows('How are conflicts resolved?', 6, 10) %>%
    group_rows('What punishments do they use?', 11, 14) %>%
    group_rows('How are repeated violations punished?', 15, 17) %>%
    group_rows('How are costs distributed?', 18, 21) %>%
    group_rows('How often will the agreement be renegotiated?', 22, 26))
}

table_mm(mms, capt = 'Marginal Means -- Full Dataset')
```

The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.

@@

```{r codefig3}
## Marginal means by Country

# Argentina
arg <- mm(subset(cj, countryOrigin=='Argentina'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(arg, capt = 'Marginal Means -- Argentina Only')
```

>>>>

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

@@

@@

# Introduction

This appendix contains the `R` code required to replicate the results we
present in "_Casting the First Stone: Understanding Attitudes towards Lynching
in Brazil_". This file also includes the descriptive statistics of our sample,
the average marginal component effects (AMCEs) for our conjoint experiment,
additional subgroup analyses for all three experiments, and a standard report
which follows APSA's guidelines for experimental research [@gerber2014reporting].

The code below loads the required datasets and the `R` packages we use in our
statistical analyses. It also translates the names of the factor variables from
Portuguese into English.

\footnotesize
```{r loading, warning=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Load the dataset, remove unused rows and columns,
# and convert variable names to snake case
df <- read_csv("../data/data.csv") %>%
  clean_names() %>%
  mutate(response_id            = as.character(response_id),
         consent                = as.factor(q1),
         progress               = as.numeric(progress),
         finished               = as.factor(finished),
         age                    = as.numeric(q2),
         gender                 = as.factor(q3),
         race                   = as.factor(q4),
         education              = as.factor(q5),
         region                 = as.factor(q6),
         household_income       = as.factor(q7),
         ideology               = as.factor(q8),
         death_penalty          = as.factor(q9),
         previous_victim        = as.character(q10),
         previous_victim_text   = as.character(q10_text),
         views_police           = as.factor(q11),
         views_justice          = as.factor(q12),
         exp02_control          = as.numeric(q18),
         exp02_police           = as.numeric(q19),
         exp02_slow_justice     = as.numeric(q20),
         exp02_small_punishment = as.numeric(q21),
         exp03_control          = as.numeric(q22),
         exp03_constitution     = as.numeric(q23),
         exp03_rights           = as.numeric(q24),
         exp03_vendetta         = as.numeric(q25)) %>%
  slice(-1L) %>%
  select(-c(q1:q12, q18:q25)) %>%
  relocate(response_id, consent, progress, finished,
           location_latitude, location_longitude) %>%
  mutate(across(where(is.character), tolower)) %>%
  mutate(across(where(is.factor), tolower))

# Translate factor values from Portuguese to English
df <- df %>%
  mutate(consent = recode(consent,
                          "concordo"     = "Agree",
                          "não concordo" = "Disagree"),
         gender = recode(gender,
                         "feminino"              = "Female",
                         "masculino"             = "Male",
                         "outro"                 = "Other",
                         "prefiro não responder" = "Rather Not Say"),
         race = recode(race,
                       "amarela"               = "Asian",
                       "branca"                = "White",
                       "indígena"              = "Indigenous",
                       "outra"                 = "Other",
                       "parda"                 = "Mixed Race",
                       "prefiro não responder" = "Rather Not Say",
                       "preta"                 = "Black"),
         education = recode(education,
                            "da 1ª à 4ª série do ensino fundamental (antigo primário)" = "Primary School",
                            "da 5ª à 8ª série do ensino fundamental (antigo ginásio)"  = "Secondary School",
                            "ensino médio (antigo 2º grau)"                            = "High School",
                            "ensino superior"                                          = "College",
                            "mestrado ou doutorado"                                    = "Graduate School",
                            "não sei"                                                  = "Don't Know"),
         region = recode(region,
                         "centro-oeste" = "Center-West",
                         "nordeste"     = "Northeast",
                         "norte"        = "North",
                         "sudeste"      = "Southeast",
                         "sul"          = "South"),
         household_income = recode(household_income,
                                   "acima de r$ 20.000"       = "Above R$20,000",
                                   "até r$ 1.000"             = "Up to R$1,000",
                                   "de r$ 1.001 a r$ 2.000"   = "From R$1,001 to R$2,000",
                                   "de r$ 10.000 a r$ 20.000" = "From R$10,001 to R$20,000",
                                   "de r$ 2.001 a r$ 3.000"   = "From R$2,001 to R$3,000",
                                   "de r$ 3.001 a r$ 5.000"   = "From R$3,001 to R$5,000",
                                   "de r$ 5.001 a r$ 10.000"  = "From R$5,001 to R$10,000"),
         ideology = recode(ideology,
                           "centro"                = "Center",
